\documentclass[a4paper,11pt,oneside]{book}
%\documentclass[12pt,openright,twoside,a4paper,brazil]{abntex2}
%\usepackage[alf]{abntex2cite}

\usepackage{color}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[brazilian]{babel}
\usepackage[hmargin=2cm,vmargin=3.5cm,bmargin=2cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{float}

\usepackage{multirow}
\usepackage{caption}
\usepackage{subcaption}

% Global configuration
\setcounter{secnumdepth}{3}		% Add level 3 of sections (can use \subsubsection in books)

% New commands
\newcommand{\todo}[1]{\null \fbox{NOTA: \textcolor{red}{#1}}  \null}

\begin{document}

\author{Gustavo Müller Nunes}
\title{Histograma de orientação de gradientes para poses de mão em um ambiente automotivo}
\date{June 2014}

\maketitle
\tableofcontents 	% Índice de conteúdos
\listoftables 		% Lista de tabelas
\listoffigures 		% Lista de figuras

%\chapter{Artigos}
%\input{section.artigos.tex}
\input{chapter.introducao.tex}
\input{chapter.referencial.teorico.tex}
%\chapter{Revisão de Literatura}
%\input{section.momento.tex}
%\input{chapter.xxx.tex}
%\chapter{Resultados e discussão}
%\chapter{Conclusão}

\begin{thebibliography}{2}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Gesture Components for Natural Interaction with In-Car devices
% 2001 / Alemanha
\bibitem{ref1} Zobl, M., Nieschulz, R., Geiger, M., Lang M., Rigoll, G.,{Gesture Components for Natural Interaction with In-Car devices}, 2003.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Gesture control for use in auto-mobiles
% 2000 / Alemanha
\bibitem{ref2} Akyol, S., Canzler, U., Bengler, K., Hahn, W.: Gesture control for use in auto-mobiles. In: Proceedings, MV A 2000 Workshop on Machine Vision Applications, Tokyo, Japan, November 28-30, 2000, IAPR, ISBN 4-901122-00-2 (2000)

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Artigos da Mitsubishi
\bibitem{ref3} W. T. Freeman and M. Roth. Orientation histograms for hand gesture recognition. Intl. Workshop on Automatic Face and Gesture-Recognition, IEEE Computer Society, Zurich, Switzerland, pages 296–301, June 1995.
\bibitem{ref4} W. T. Freeman, K. Tanaka, J. Ohta, and K. Kyuma. Computer vision for computer games. 2nd International Conference on Automatic Face and Gesture Recognition, Killington, VT, USA, pages 100–105, October 1996.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Real-time Vision-based Infotainment User Determination for Driver Assistance
% 2008 / Estados Unidos
% Artigo com câmera infra no carro e uso de HOG e SVM.
% Criou sua própria base de dados (4 horas diferentes do dia com 8 individuos).
% Possue um descrição do SVM que pode ser usada no futuro.
% [8] Descritor de mão usando Haar-wavelet.
% [9] Detecção de mão usando imagens térmicas.
% [10] Referência ao SIFT. 
\bibitem{ref5} Shinko Y. Cheng and Mohan M. Trivedi. Real-time Vision-based Infotainment User Determination for Driver Assistance, IEEE Intelligent Vehicles Symposium, June 4-6, 2008

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% An Effective Crossing Cyclist Detection on a Moving Vehicle 
% 2010 / China
% Tem a formula da normalizacao
% [10] No overlap HOG local features / Mais informação de como calcular o HOG
\bibitem{ref6} An Effective Crossing Cyclist Detection on a Moving Vehicle

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Hand-gesture recognition: comparative study of global, semi-local and local approaches
% 2011 / França
% A base de dados não é pública.
% [6] Descrição do SIFT.
\bibitem{ref7} Hand-gesture recognition: comparative study of global, semi-local and local approaches

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Automatic Ship Recognition Robust Against Aspect Angle Changes and Occlusions
% 2012 / Japão - Laboratório da Toshiba
% [6] Referência sobre coHOG
\bibitem{ref8} Automatic Ship Recognition Robust Against Aspect Angle Changes and Occlusions

\bibitem{ref9} An Extended HOG Model: SCHOG for Human Hand Detection

% A ROBUST METHOD OF FINGERTIP DETECTION IN COMPLEX BACKGROUND
% 2012 / China - Nokia
% [12] Verificar metodo de Viola & Jones
% [14] Referência para HOG
\bibitem{ref10} A ROBUST METHOD OF FINGERTIP DETECTION IN COMPLEX BACKGROUND

\bibitem{ref11} Deformable HOG-based Shape Descriptor

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Gesture-based control of in-car devices
% Ainda não consegui baixar
\bibitem{ref12} Zobl, M., Geiger, M., Morguet, P., Nieschulz, R., Lang, M.: Gesture-based control of in-car devices. In: VDI-Berichte 1678: USEWARE 2002 Mensch-Maschine-Kommunikation/Design, GMA Fachtagung USEWARE 2002, Darmstadt, Germany, June 11-12, 2002, Dusseldorf, VDI, VDI-Verlag (2002) 305–309

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% A usability study on hand gesture controlled operation of in-car devices
% Artigo de justificativa (usabilidade)
\bibitem{ref13} Zobl, M., Geiger, M., Bengler, K., Lang, M.: A usability study on hand gesture controlled operation of in-car devices. In: Abridged Proceedings, HCI 2001 9th Int. Conference on Human Machine Interaction, New Orleans, Louisiana, USA, August 5-10, 2001, New Jersey, Lawrence Erlbaum Ass. (2001) 166–168

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Intermodal differences in distraction eﬀects while controlling automotive user interfaces
% Artigo de justificativa (usabilidade)
\bibitem{ref14} Geiger, M., Zobl, M., Bengler, K., Lang, M.: Intermodal differences in distraction effects while controlling automotive user interfaces. In: Proceedings Vol. 1: Usability Evaluation and Interface Design , HCI 2001 9th Int. Conference on Human Machine Interaction, New Orleans, Louisiana, USA, August 5-10, 2001, New Jersey, Lawrence Erlbaum Ass. (2001) 263–267

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Distinctive Image Features from Scale-Invariant Keypoints
% Descrição do SIFT.
\bibitem{ref15} D. G. Lowe, “Distinctive image features from scale-invariant keypoints,” Int. J. Comput. Vis., vol. 60, no. 2, pp. 91–110, Nov. 2004. 

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% A vision-based system for automatic hand washing quality assessment
% Estudar o que é "one-against-one multi class SVM"
\bibitem{ref16} "A vision-based system for automatic hand washing quality assessment"

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Histograms of Oriented Gradients for Human Detection
\bibitem{dalal} Dalal, N. and Triggs, M, "Histograms of Oriented Gradients for Human Detection", in Proc. Of IEEE CVPR2005, vol. 1, pp. 886-893, June 2005.

\bibitem{kinect} http://www.microsoft.com/en-us/kinectforwindows/develop/
\bibitem{intel} http://software.intel.com/en-us/vcsource/tools/perceptual-computing-sdk

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Referências de jornal e revistas
\bibitem{news:kinect_sales} http://www.microsoft.com/en-us/news/features/2013/feb13/02-11xbox.aspx
\bibitem{mercedes_youtube} https://www.youtube.com/watch?v=OQkdvi55woA
\bibitem{mercedes_safety} http://www.mbusa.com/mercedes/benz/safety
\end{thebibliography}


\end{document}